### 2010-06-25 trunk/paper/IIWAS2010/content/related_work.tex
fri meeting comments

\subsection{Ontology generators}

@@

Moreover, YAGO type extraction is mainly based on the assumption that
each Wikipedia page has at least one tagged category, and the assigned Wikipedia
categories are relevant to that Wikipedia page. The Wikipedia page category
assignments are subjectively assigned by human editors and some Wiki pages are
unassigned i.e., they have no category. In addition, we cannot completely rely
on the relevance of these assigned Wikipedia page categories.

\subsection{NLP Interfaces}

>>>>

Question Answering (QA) is an old field and there has been a recent influx of QA work. The earliest question answering systems include BASEBALL \cite{Green1961} and Lunar \cite{woods1973} were both \emph{closed domain} and \emph{closed corpus}.  Closed domain QA systems are those in which the possible meanings of the questions given are finite. We define closed corpus sytems as those in which the sources used to answer questions are finite.  QA systems that treat the web as a document collection is considered an open corpus system.  The morpheus system is considered an open corpus system.  It goes beyond current state of the art QA systems by examining deep web sources.

Several community QA systems have been developed, one of the most popular being Yahoo! Answers \cite{yahooanswers2008}.  These sites enlist a community of users to answer question posed by other users.  This idea has evolved to invent socially integrated QA systems have emerged such as Aardvark \cite{vark2010}. In addition to having questions answered by users, aardvark is able to contact potential answers through several mediums beyond its webpage (e.g. instant message, mobile phone).  This allows for a possibly faster answers to questions.  The morpheus system relies on both user interface and the property of similar question being answered by a community of users to give a fast reliable answer.

\subsection{Ontology generators} 
\label{sec:ontology_generators}

@@

However, YAGO type extraction is mainly based on the assumption that
each Wikipedia page has at least one tagged category, and the assigned Wikipedia
categories are relevant to that Wikipedia page. The Wikipedia page category
assignments are subjectively assigned by human editors and some Wiki pages are
unassigned i.e., they have no category. In addition, we cannot completely rely
on the relevance of these assigned Wikipedia page categories.

%\subsection{NLP Interfaces}

### 2010-06-25 trunk/paper/IIWAS2010/content/results_discussion.tex
fri meeting comments

\subsection{Discussion}

>>>>

We used this top category of each of the terms in the candidate SSQ and
determined the category divergence with the qualified SSQ categories in the QRM
store. We assumed that all of them belong to the same realm or domain (but, it
is different in real time). In the end, we combine the divergence measure and
ranked QRMs based on the relevance score. The table \ref{tbl:ranked_queries}
shows the top ranked queries that belong to the QRMs in store for the above
query.

\begin{tabular}{l | r}
Query & Score\\
\hline
The tire size of a 1997 Toyota Camry V6 is what? & 0.11\\ 
\hline
\end{tabular}

\caption{Top ranked queries and their relevance score}
\label{tbl:ranked_queries}

%\subsection{Discussion}
\section{Conclusion}
This query matching strategy assumes that query terms are available in the
category corpus. The candidate query's category annotation will fail if the
query terms are not available in the corpus. We are working on improving this
approach by using a probabilistic approach as used in the Topic
Models\cite{Blei2003latentdirichlet}. Similarly, the Morpheus ontology building
process needs categorized web pages. As explained in section
\ref{sec:ontology_generators}, the Wikipedia page categories have some
limitations for this purpose. Without a super vision, the page categorization is
often a challenging problem, because topics in the pages that belong to a realm
(e.g. automotive) usually overlap. So we are experimenting the applicability of
probabilistic topic models into this web page categorization, and automatic
generation of a realm-ontology based on the topics being extracted.
